% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      


First of all, I would like to thank my supervisor Vasily Zaburdeav and Frank J\"{u}licher for offering me the opportunity to work as a PhD student in MPI-PKS. 
I thank them for the guidance along my whole PhD project. I was influenced by the prudent scientific attitude from both Frank and Vasily. Thank for the uncountable and inevalueble advices during my PhD study. Beside science, I also want to thank them for building up a the enjoylable atmosphere for day life in the MPI-PKS.


And I would like to thank my coorperators who helps me a lot during my PhD project. Specially, I would like to thank Yen Ting Lin, who worked with me since the begining of the project. As a former posdoc in our group, he taught me many useful knowledge and skills. As a good friend, he shared me a lot of his experences.There are so many joys working togother with him. I also want to express my deep thank to Daniela Froemberg and Jaeoh Shin, who directly coorperated with me on my PhD project. And Sergey Denisov who helped me to initialize my simulations. Thanks to our experimental cooperators Mariola Chac\'{o}n, Petrina Delivani and Iva Toli\'{c} in Max Planck Institute of Molecular Cell Biology and Genetics for proposing such an interesting biological problem and all supports from biological side. I also want to thank Yu Zhou, as a good friend and cooperator, we enjoyed all of our time together in MPI-PKS. Thanks to all the other wonderful group members in Biophysics Division of MPI-PKS, Wolfram Poenisch, Lennart Hilbert, Hui-Shun Kuan, Christoph A. Weber, Jens Karschau, Andr\'{e} Scholich, Marko Popovic, Alexander Mietke et al. for the fruitful discussions. 

    Finally, I would like to thank my families. Without their supports, my study in MPI-PKS is not even possible to happen. Aslo I want to thank to the all the Chinese colleges in MPI-PKS. The life of study abroad is so sweet with them together.



\end{acknowledgements}

